Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=$10$.

\medskip
Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},

\begin{equation}   
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation}

>>>>

Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.

\medskip
Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. They conducted a sensitivity study to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},   
\begin{equation}   
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation}

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
\hspace{0.5cm}      
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
\vspace{0.cm}
\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c.pdf}
      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{5.cm} (e)t=10.00s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{cm.s}^{-1}\right)$ showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
\hspace{0.5cm}      
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
\vspace{0.cm}
\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c.pdf}
      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{5.cm} (e)t=10.00s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{in cm.s}^{-1}\right)$ showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage
